Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
note on the definition of IPT
comment on figure 4

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/clusterAnalysis.png}
\caption{Cluster analysis of the similarity judgments. $j/I$ and $j/Pt$ compare the partition obtained using the similarity judgments clustered using a growing number of clusters versus respectively the instrument partition and the playing technique partition. Normalizing null partitions based NMI $nullI$ and $nullPt$ are used to obtain normalized measures: $nj/I$ and $nj/Pt$.}
\label{fig:clusters}
\end{figure}

>>>>

\vl{It should be made very clear that the IPT taxonomy is
the set product of the instrument taxonomy
and the playing technique taxonomy. @writing}

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/clusterAnalysis.png}
\caption{Cluster analysis of the similarity judgments. $j/I$ and $j/Pt$ compare the partition obtained using the similarity judgments clustered using a growing number of clusters versus respectively the instrument partition and the playing technique partition. Normalizing null partitions based NMI $nullI$ and $nullPt$ are used to obtain normalized measures: $nj/I$ and $nj/Pt$.
\vl{This line plot is very hard to understand.
The legend box occludes the data on the top-right corner.
It would be preferable to remove this legend box and label lines
by placing text upon them,
so that the plot would be legible to readers with color vision deficiencies.
Besides, the choice of line labels is cryptic, as it relies on abbreviations.
The NMI abbreviation should be expanded.
@figure}}
\label{fig:clusters}
\end{figure}
